2.1 APL Data Quality Check with additonal cleaning

### 2023-12-05 2_scripts/2.1 APL Data Quality Check.qmd
Add RG Adj Scripts

# Results
table(RFD4682_e$`N-IgG_INTERP`, useNA = 'ifany')
```
#### Calculate positivity directly

```{r}
# Create month var
RFD4682_e$Col_Date<-RFD4682_e$COLLECTION_DATE %>%
  as.Date(., tz="UTC") # a short time var, date only

library(lubridate)
library(zoo)

# Only keep the month, remove the data
RFD4682_e$mois <- month(RFD4682_e$Col_Date)
RFD4682_e$annee <- year(RFD4682_e$Col_Date)
RFD4682_e$Col_Month<-paste(RFD4682_e$annee, RFD4682_e$mois, 
                           sep = "-")
table(RFD4682_e$Col_Month, useNA='ifany')
# as char variable if needed for calculation, use as.yearmon() from {zoo} or just use the Col_Date var
```

```{r}
# Calculate positivity for each month
tb1<-RFD4682_e[is.na(RFD4682_e$`N-IgG_RESULT`)==F,] %>%
  group_by(Col_Month) %>%
  summarise(n = n())

tb2<-RFD4682_e[RFD4682_e$`N-IgG_INTERP`=="Positive",] %>%
  group_by(Col_Month) %>%
  summarise(n.pos = n())

tb1<-merge(tb1, tb2, by = "Col_Month", all.x = T, all.y = F)
tb1$prop.n<-tb1$n.pos/tb1$n
tb1$Col_Month<-as.yearmon(tb1$Col_Month)
tb1<-tb1[order(tb1$Col_Month),]

# Add R-G adjusted prevalances
# Sen=0.881, Spec = 0.947
# Source:
tb1$prop.n_RG<- (tb1$prop.n+0.881-1)/(0.881+0.947-1)

# remove NAs
tb1<-tb1[!is.na(tb1$Col_Month),]

tb1 %>%
  with(plot(y=.$prop.n, x = .$Col_Month, type="b",
            ylab="positivity", xlab="Month",col="blue")
       )
```

#### Apply ggplot, plot two together
```{r}
tb1_melt<-melt(select(tb1, Col_Month, prop.n, prop.n_RG), id.vars = "Col_Month")

tb1_melt %>%
  ggplot(aes(x=Col_Month, y=value, colour=variable)) +
  geom_point(aes(colour=variable)) +
  geom_line(aes(colour=variable))  +
  theme_bw()
```

```{r}

plot(x=temp$Time ,y=temp$Positivity, type = 'b', 
     col="blue", xlab="Time: 2022", ylab="Test Positivity",
     main="Anti-N Assay Positivity in Omicron Wave, using APL Data")
plot(x=temp$Time ,y=temp$Positivity_RG, 
     type = 'b', col="red")
```

>>>>

# Results
table(RFD4682_e$`N-IgG_INTERP`, useNA = 'ifany')
```

#### Add a year-month var
```{r}
# only keep the month, remove the data
RFD4682_e$Col_Month<-format(as.Date(RFD4682_e$COLLECTION_DATE), "%Y-%m")
table(RFD4682_e$Col_Month, useNA='ifany')

# as char variable if needed for calculation, use as.yearmon() from {zoo} or just use the Col_Date var
```

#### Save a cleaned ver of RFD4682e
```{r}
save(RFD4682_e, file = "../1_data/private/RFD4682e.RData")
```
